---
title       : Coursera Course Pitch
subtitle    : univariate analysis - linear model
author      : Benjamin Knoeferl
date        : 01.31.2016
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Content

These slides are part of the coursera class "developing data products".

The project consists of two tasks:

* Create a shiny app
* Create a pitch using RStudio's Presenter or Slidify


--- .class #id 

## Purpose of the App

Very often it appears, that one would like to make a univariate data analysis in form of a linear model without using a statistical tool.

With this app, the user is able to select a semikolon delimited csv file containing 6 variables (1 outcome, and 5 explanatory variables).

At the top, he can see the dataframe, below, a histogramm of the variable he selects and at the bottom, the model output of a univariate linear model.

Dataframe has to be structured in following format:
* Column 1: Outcome
* Column 2-6: explanatory variables

The User is also able to change the histogram's breaks (from 1 to 50)


---




## Data

* test data used for this application is generated in R using rnorm() function.
* dataframe containing 5 variables (a,b,c,d,e) as well as one outcome y dependent on those

```{r}

a <- rnorm(1000, mean=10, sd=2)
b <- rnorm(1000, mean=100, sd=10)
c <- rnorm(1000, mean=0, sd=2)
d <- rnorm(1000, mean=7, sd=3)
e <- rnorm(1000, mean=25, sd=2)

y <- 2*a + 4*b - 3*c + 0.5*d + e + rnorm(1000)

dat <- as.data.frame(cbind(y, a, b, c, d, e))
```

---

## R Code embedded

```{r simple-plot, fig.height = 6, fig.align = 'center', message = F}

dat <- read.csv("C:\\Users\\bknoeferl\\Desktop\\test_data.csv", header=TRUE, sep=";", dec=",")
hist(dat$a, breaks=30, col="green")
```
